---
title: "Dowloading Diversity Data"
author: "1st Author"
date: "2023-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Here we are downloading the diversity data from neon and cleaning it
#### Download and load necessary libraries
```{r}
install.packages("tidyverse")
install.packages("neonUtilities")
install.packages("multcomp")
install.packages("dplyr")
install.packages("janitor")
install.packages("vegan")

#Load libraries
library(neonUtilities)
library(dplyr)
library(tidyverse)
library(neonUtilities)
library(multcomp)
library(janitor)
library(vegan)
```

##### Download Beetle data using neonUtilities packages
```{r, eval = FALSE, echo = FALSE}
beetle_data = loadByProduct(dpID = "DP1.10022.001", 
                            site= c("BONA", "CLBJ", "DEJU", "GUAN", "HARV", "KONZ", "LENO", "MLBS","NIWO", "ONAQ", "ORNL", "OSBS", "SCBI", "SJER", "SOAP", "TALL", "UKFS", "UNDE", "WREF","YELL", "ABBY", "BART", "BLAN", "DELA",  "GRSM", "HEAL", "JERC", "MOAB", "TEAK", "PUUM", "SERC", "RMNP","STEI", "TREE"),
                            startdate = "2013-01", enddate = "2022-12",
                            check.size = FALSE)
```

##### Extract expert taxonomic ID from data list
```{r}
beetle_full_data = beetle_data$bet_expertTaxonomistIDProcessed

#Remove rows where siteID and taxon ID says NA
beetle_full_data = beetle_full_data %>% drop_na(taxonID)
beetle_full_data = beetle_full_data %>% drop_na(siteID)
```

##### Write beetle total diversity that includes taxonomic information and field information
```{r}
write.csv(beetle_full_data, "beetle_full_data.csv", row.names = FALSE)
```

##### Download bird data
```{r}
bird_data= loadByProduct(dpID = "DP1.10003.001", 
              site= c("BONA", "CLBJ", "DEJU", "GUAN", "HARV", "KONZ", "LENO", "MLBS","NIWO", "ONAQ", "ORNL", "OSBS", "SCBI", "SJER", "SOAP", "TALL", "UKFS", "UNDE", "WREF","YELL", "ABBY", "BART", "BLAN", "DELA",  "GRSM", "HEAL", "JERC", "MOAB", "TEAK", "PUUM", "SERC", "RMNP","STEI", "TREE"),
              startdate = "2013-01", enddate = "2022-12",
              check.size = FALSE)

```

##### Extract expert taxonomic ID from data list
```{r}
#Download brd_countdata table and bird_fielddata (metadata) from list of beetle field data
bird_taxa = bird_data$brd_countdata

bird_fieldData = bird_data$brd_perpoint
```

#Merge taxonomic and field data by namedLocation
```{r}
bird_full_data = merge(bird_taxa, bird_fieldData,
                   by = c("eventID", "pointID", "uid", "plotID", "siteID", "domainID", "release",
                          "plotType", "startDate", "namedLocation", "publicationDate") ,
                   all = TRUE, check.duplicates = FALSE)

#Remove rows where taxon ID says NA
#This will have the same contents as the bird taxa dataframe,
#with added columns from field table
bird_full_data = bird_full_data %>% drop_na(taxonID)
```

##### Write bird presence data that includes taxonomic information and field information to csv
```{r}
write.csv(bird_full_data, "bird_full_data.csv", row.names = FALSE)
```

###### This code uses Plant presence and percent cover data from NEON https://data.neonscience.org/data-products/DP1.10058.001
####### Download and load necessary packages
###### Download plant data selected forested sites using neonutilities for each site
```{r, error = T}
plant_data = loadByProduct(dpID = "DP1.10058.001", 
              site= c("BONA", "CLBJ", "DEJU", "GUAN", "HARV", "KONZ", "LENO", "MLBS","NIWO", "ONAQ", "ORNL", "OSBS", "SCBI", "SJER", "SOAP", "TALL", "UKFS", "UNDE", "WREF","YELL", "ABBY", "BART", "BLAN", "DELA",  "GRSM", "HEAL", "JERC", "MOAB", "TEAK", "PUUM", "SERC", "RMNP","STEI", "TREE"),
              startdate = "2013-01", enddate = "2022-12",
              check.size = FALSE)

#For metadata purposes, extract the tables we will be merging and write to csv
plant_1m = plant_data$div_1m2Data
plant_10m_100m = plant_data$div_10m2Data100m2Data

write.csv(plant_1m, "plant_1m.csv", row.names = F)
write.csv(plant_10m_100m, "plant_10m_100m.csv", row.names = F)
```

###### Extract expert taxonomic ID from data list using function.
###### This chunk was obained from: https://github.com/admahood/neonPlantEcology/blob/master/R/diversity_data_prep.R
Citation: Adam Mahood. (2021). admahood/neondiveRsity: Added betadiversity and dissolve_years options (v1.2.5). Zenodo. https://doi.org/10.5281/zenodo.5261104
```{r}
get_longform_cover <- function(neon_div_object,
                               trace_cover=0.5,
                               scale = "plot",
                               dissolve_years = FALSE,
                               fix_unks = FALSE){
  require(dplyr)
  require(tidyr)
  require(stringr)
  require(magrittr)
  if(scale == "plot"){
    cover <- neon_div_object$div_1m2Data %>%
      dplyr::mutate(endDate = as.Date(endDate)) %>%
      dplyr::filter(divDataType == "plantSpecies") %>%
      dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
      tidyr::replace_na(list(percentCover=trace_cover)) %>%
      dplyr::group_by(plotID, subplotID, taxonID, year) %>%
      # dealing with the multiple bout issue by first getting the max cover
      # per sampling effort
      dplyr::summarise(cover = max(percentCover),
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()  %>%
      dplyr::filter(taxonID != "") %>%
      dplyr::group_by(plotID, taxonID, year) %>%
      dplyr::summarise(cover = sum(cover, na.rm=TRUE)/8,
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()
    
    traces <- neon_div_object$div_10m2Data100m2Data %>%
      dplyr::mutate(endDate = as.Date(endDate)) %>%
      dplyr::filter(targetTaxaPresent == "Y") %>%
      dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
      dplyr::group_by(plotID, subplotID, taxonID, year) %>%
      dplyr::summarise(cover = trace_cover,
                       scientificName = first(scientificName),
                       nativeStatusCode = first(nativeStatusCode),
                       family = first(family)) %>%
      dplyr::ungroup() %>%
      dplyr::filter(taxonID != "") %>%
      dplyr::group_by(plotID, taxonID, year) %>%
      dplyr::summarise(cover = sum(cover, na.rm=TRUE)/12,
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()
    
    full_on_cover <- dplyr::bind_rows(cover, traces) %>%
      dplyr::group_by(plotID, taxonID, year, nativeStatusCode, scientificName, family) %>%
      dplyr::summarise(cover = sum(cover)) %>%
      dplyr::ungroup()%>%
      dplyr::mutate(site = str_sub(plotID, 1,4),
                    subplotID = "plot")
    if(fix_unks) full_on_cover <- full_on_cover %>%  unk_fixer()
    
    if(dissolve_years) {
      year_range <- unique(full_on_cover$year)%>%
        as.numeric %>%
        range %>%
        paste(collapse = "-")
      n_years <- length(unique(full_on_cover$year))
      full_on_cover <- full_on_cover %>%
        dplyr::group_by(plotID, taxonID, nativeStatusCode, scientificName, family, site, subplotID) %>%
        dplyr::summarise(cover = sum(cover, na.rm=T)/n_years) %>%
        dplyr::ungroup() %>%
        dplyr::mutate(year = year_range)
    }
    
    return(full_on_cover)
  }
  if(scale == "site"){
    cover <- neon_div_object$div_1m2Data %>%
      dplyr::mutate(endDate = as.Date(endDate)) %>%
      dplyr::filter(divDataType == "plantSpecies") %>%
      dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
      tidyr::replace_na(list(percentCover=trace_cover)) %>%
      dplyr::group_by(plotID, subplotID, taxonID, year) %>%
      # dealing with the multiple bout issue by first getting the max cover
      # per sampling effort
      dplyr::summarise(cover = max(percentCover),
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()  %>%
      dplyr::filter(taxonID != "") %>%
      dplyr::group_by(plotID, taxonID, year) %>%
      dplyr::summarise(cover = sum(cover, na.rm=TRUE)/8,
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()
    
    traces <- neon_div_object$div_10m2Data100m2Data %>%
      dplyr::mutate(endDate = as.Date(endDate)) %>%
      dplyr::filter(targetTaxaPresent == "Y") %>%
      dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
      dplyr::group_by(plotID, subplotID, taxonID, year) %>%
      dplyr::summarise(cover = trace_cover,
                       scientificName = first(scientificName),
                       nativeStatusCode = first(nativeStatusCode),
                       family = first(family)) %>%
      dplyr::ungroup() %>%
      dplyr::filter(taxonID != "") %>%
      dplyr::group_by(plotID, taxonID, year) %>%
      dplyr::summarise(cover = sum(cover, na.rm=TRUE)/12,
                       nativeStatusCode = first(nativeStatusCode),
                       scientificName = first(scientificName),
                       family = first(family)) %>%
      dplyr::ungroup()
    
    n_plots <- length(unique(cover$plotID))
    
    full_on_cover <- dplyr::bind_rows(cover, traces) %>%
      dplyr::group_by(plotID, taxonID, year, nativeStatusCode, scientificName, family) %>%
      dplyr::summarise(cover = sum(cover)) %>%
      dplyr::ungroup()%>%
      dplyr::mutate(site = str_sub(plotID, 1,4)) %>%
      dplyr::group_by(site, taxonID, year, nativeStatusCode, scientificName, family) %>%
      dplyr::summarise(cover = sum(cover)/n_plots) %>%
      dplyr::mutate(subplotID = "site",
                    plotID = "site") %>%
      dplyr::ungroup()
    if(fix_unks) full_on_cover <- full_on_cover %>%  unk_fixer()
    if(dissolve_years) {
      year_range <- unique(full_on_cover$year)%>%
        as.numeric %>%
        range %>%
        paste(collapse = "-")
      n_years <- length(unique(full_on_cover$year))
      full_on_cover <- full_on_cover %>%
        dplyr::group_by(plotID, taxonID, nativeStatusCode, scientificName, family, site, subplotID) %>%
        dplyr::summarise(cover = sum(cover, na.rm=T)/n_years) %>%
        dplyr::ungroup() %>%
        dplyr::mutate(year = year_range)
    }
    return(full_on_cover)
  }
  
  cover8 <- neon_div_object$div_1m2Data %>%
    dplyr::mutate(endDate = as.Date(endDate)) %>%
    dplyr::filter(divDataType == "plantSpecies") %>%
    dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
    # entries in the df with no values but species was there
    # i.e. someone put the sp. code and forgot to fill in the number
    # putting as trace cover value
    tidyr::replace_na(list(percentCover=trace_cover)) %>%
    dplyr::mutate(endDate = as.Date(endDate)) %>%
    dplyr::filter(divDataType == "plantSpecies") %>%
    dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
    dplyr::group_by(plotID, subplotID, taxonID, year) %>%
    # dealing with the multiple bout issue by first getting the mean cover
    # per sampling effort, without aggregating, then later we'll aggregate.
    # that way, a fall-bloomer that isn't visible in spring, for example,
    # will be given its full cover value for fall, but then a species
    # that is there for both seasons will be averaged, if that makes sense
    dplyr::summarise(cover = max(percentCover),
                     nativeStatusCode = first(nativeStatusCode),
                     scientificName = first(scientificName),
                     family = first(family)) %>%
    dplyr::ungroup()  %>%
    dplyr::filter(taxonID != "") %>%
    dplyr::mutate(subplotID = str_sub(subplotID, 1, 4))
  
  
  # 10m2,100m2 are given 0.5 (we can change later)
  # unique(x$div_10m2Data100m2Data$subplotID) # there are 12 subplots
  
  traces8 <- neon_div_object$div_10m2Data100m2Data %>%
    dplyr::mutate(endDate = as.Date(endDate)) %>%
    dplyr::filter(targetTaxaPresent == "Y") %>%
    dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
    dplyr::group_by(plotID, subplotID, taxonID, year) %>%
    dplyr::summarise(cover = trace_cover,
                     scientificName = first(scientificName),
                     nativeStatusCode = first(nativeStatusCode),
                     family = first(family)) %>%
    dplyr::ungroup() %>%
    dplyr::filter(taxonID != "",
                  subplotID != "31", # these are the 100m2 subplots under which two 1m2 and 10m2 pairs are nested
                  subplotID != "32",
                  subplotID != "40",
                  subplotID != "41")  %>%
    dplyr::mutate(subplotID = str_sub(subplotID, 1, 4))
  
  traces100s <- neon_div_object$div_10m2Data100m2Data %>%
    dplyr::mutate(endDate = as.Date(endDate)) %>%
    dplyr::filter(targetTaxaPresent == "Y") %>%
    dplyr::mutate(year = str_c(str_sub(endDate,1,4)))%>%
    dplyr::group_by(plotID, subplotID, taxonID, year) %>%
    dplyr::summarise(cover = trace_cover,
                     scientificName = first(scientificName),
                     nativeStatusCode = first(nativeStatusCode),
                     family = first(family)) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(site = str_sub(plotID, 1,4)) %>%
    dplyr::filter(taxonID != "",
                  subplotID == "31"| #These are the 100m2 subplots under which two 1m2 and 10m2 pairs are nested
                    subplotID == "32"|
                    subplotID == "40"|
                    subplotID == "41")
  
  #Aggregating at different scales 
  cover8_1m2 <- cover8 %>%
    dplyr::group_by(plotID, subplotID, taxonID, year, nativeStatusCode, scientificName, family) %>%
    dplyr::summarise(cover = sum(cover)) %>%
    dplyr::ungroup()%>%
    dplyr::mutate(site = str_sub(plotID, 1,4))
  if(fix_unks) cover8_1m2 <- unk_fixer(cover8_1m2)
  
  cover8_1m2_10m2 <- rbind(cover8, traces8) %>%
    dplyr::group_by(plotID,subplotID, taxonID, year, nativeStatusCode, scientificName, family) %>%
    dplyr::summarise(cover = sum(cover)) %>%
    dplyr::ungroup()%>%
    dplyr::mutate(site = str_sub(plotID, 1,4))
  if(fix_unks) cover8_1m2_10m2<-cover8_1m2_10m2 %>%  unk_fixer()
  
  cover4 <- cover8_1m2_10m2 %>%
    dplyr::mutate(subplotID = str_sub(subplotID, 1,2)) %>%
    dplyr::bind_rows(traces100s) %>% #Adding in the 100m2 subplots
    dplyr::group_by(plotID, subplotID, year, taxonID) %>%
    dplyr::summarise(cover = sum(cover), #This is summing together repeats from the rbinding
                     scientificName = first(scientificName),
                     nativeStatusCode = first(nativeStatusCode),
                     family = first(family),
                     site = first(site)) %>%
    dplyr::ungroup()
  if(fix_unks) cover4 <- cover4 %>%  unk_fixer()
  
  
  if(scale == "1m") full_on_cover <- cover8_1m2
  if(scale == "10m") full_on_cover <- cover8_1m2_10m2
  if(scale == "100m") full_on_cover <- cover4
  
  if(dissolve_years) {
    year_range <- unique(full_on_cover$year)%>%
      as.numeric %>%
      range %>%
      paste(collapse = "-")
    n_years <- length(unique(full_on_cover$year))
    full_on_cover <- full_on_cover %>%
      dplyr::group_by(plotID, taxonID, nativeStatusCode, scientificName, family, site, subplotID) %>%
      dplyr::summarise(cover = sum(cover, na.rm=T)/n_years) %>%
      dplyr::ungroup() %>%
      dplyr::mutate(year = year_range)
  }
  
  
  return(full_on_cover)
}

plant_full_data = get_longform_cover(plant_data)
```

###### Remove Unknown species (indicated as 2Plant in dataset)
```{r}
plant_full_data1 = plant_full_data[!grepl(c("2PLANT","2PLANT-H", "2PLANT-S"), plant_full_data$taxonID),]

write.csv(plant_full_data1, "plant_full_data.csv", row.names = FALSE)
```

