---
title: "Processing Bird, Beetle and Plant Diversity"
author: "1st Author"
date: "2023-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Here we are downloading data from neon, cleaning it, and calculating diversity
#### If you are dealing with processed data tables (ie. beetle_full_data.csv, bird_full_data.csv, etc. start on line 132)
#### Download and load necessary libraries
```{r}
install.packages("tidyverse")
install.packages("neonUtilities")
install.packages("multcomp")
install.packages("dplyr")
install.packages("janitor")
install.packages("vegan")

#Load libraries
library(neonUtilities)
library(dplyr)
library(tidyverse)
library(neonUtilities)
library(multcomp)
library(janitor)
library(vegan)
```

###### There isn't a count for beetles, more so a presence and absence data
### Goal:
##### Run species richness for each site
##### Create data frame with different species for each site
##### Pseudoabundance is how many times the species is repeated (run for each site)
##### Count number of times a unique species occurs in each site
#####Read in full df
```{r}
beetle_full_data = read.csv("input_data.files/beetle_full_data.csv")
```

```{r}
#Beetle occurrence only sorted by siteID
#Quantify beetle occurrence
#Group by specific epithet and site ID
beetle_occ = beetle_full_data %>%
  tabyl(specificEpithet, siteID, sort = TRUE)

#Show species distribution for each species for each site
beetle_occ = data.frame(t(beetle_occ))
names(beetle_occ) <- as.matrix(beetle_occ[1,])
beetle_occ = beetle_occ[-1,]
beetle_occ[] <- lapply(beetle_occ, function(x) type.convert(as.character((x))))

#The last column was empty so I removed it
beetle_occ = beetle_occ[,-467]

#Count the number of non-zero cells for each row
#This will give you the richness per site
#This will appear in the final column of the dataset
beetle_occ$count <- rowSums(beetle_occ!=0)

#Rename count as species richness
names(beetle_occ)[467] = "species_richness"


#Calculate abundance
#Sum all rows except species_richness column
row_sum = data.frame(rowSums(beetle_occ[, -467]))

#rename column
names(row_sum)[1] = "total_organism"

#rename 0th column
beetle_occ<-tibble::rownames_to_column(beetle_occ, "siteID") 

#rename 0th column
row_sum<-tibble::rownames_to_column(row_sum, "siteID") 

#merge row_sum dataframe with beetle_occ dataframe by 
beetle_occ = merge(beetle_occ, row_sum,
                   by = "siteID",
                   all = TRUE, check.duplicates = FALSE)

#This table contains occurrence and richness values (last 2 columns)
```


###### Write Occurrence data to CSV file.
```{r}
write.csv(beetle_occ, "beetle_occ.csv", row.names = FALSE)
```

###### Import csv of site data from: https://www.neonscience.org/field-sites/explore-field-sites
```{r}
site_info = read.csv("NEON_Field_Site_Metadata_2021.csv")

# Select interest sites
site_info = site_info[site_info$field_site_id %in% c("BONA", "CLBJ", "DEJU", "GUAN", "HARV", "KONZ", "LENO", "MLBS","NIWO", "ONAQ", "ORNL", "OSBS", "SCBI", "SJER", "SOAP", "TALL", "UKFS", "UNDE", "WREF","YELL", "ABBY", "BART", "BLAN", "DELA",  "GRSM", "HEAL", "JERC", "MOAB", "TEAK", "PUUM", "SERC", "RMNP","STEI", "TREE"), ]

#Merge info for interest site with data
beetle_field_data = merge(beetle_occ, site_info, by.x = "siteID", by.y = "field_site_id")

#Import table into GIS and Make layers in GIS with species richness and total
#number of species. This helps to visualize diversity.
#Still have to figure out of to graph it
```


###### Create another dataframe which contains diversity information
###### Calculate Diversity indices using the Vegan Package in R
```{r}
beetle_full_data = read.csv("input_data_files/beetle_full_data.csv")

beetle_sp_div = t(beetle_full_data %>%
  tabyl(specificEpithet, siteID, sort = TRUE))

#Convert to Data frame 
beetle_sp_div = data.frame(beetle_sp_div)


#Place specific epithet as row titles
names(beetle_sp_div) <- as.matrix(beetle_sp_div[1,])
beetle_sp_div = beetle_sp_div[-1,]
beetle_sp_div[] <- lapply(beetle_sp_div, function(x) type.convert(as.character((x))))
```

#Calculate Diversity Indices
```{r}
beetle_sp_div = beetle_sp_div[,c(1:466)]

#Simpson Diversity
simpson_diversity = data.frame(diversity(beetle_sp_div, "simpson"))
simpson_diversity <-tibble::rownames_to_column(simpson_diversity, "siteID") 

#Shannon Diversity
shannon_diversity = data.frame(diversity(beetle_sp_div, "shannon"))
shannon_diversity <-tibble::rownames_to_column(shannon_diversity, "siteID") 

#Calculate Chao1 diversity
chao_ace = as.data.frame(estimateR(beetle_sp_div))
chao_ace = t(chao_ace)
colnames(chao_ace)[2] = "Chao1_Beetle"
colnames(chao_ace)[4] = "ACE_Beetle"
chao_ace = as.data.frame(chao_ace[,c(2,4)])
chao_ace = tibble::rownames_to_column(chao_ace, "siteID") 

richness <- as.data.frame(rowSums(beetle_sp_div!=0))
colnames(richness)[1] = "Richness_Beetle"

#Merge all diversity tables

diversity_index = merge(shannon_diversity, simpson_diversity, by = "siteID")

names(diversity_index)[2] = "Shannon_Beetle"
names(diversity_index)[3] = "Simpson_Beetle"

diversity_index = merge(diversity_index, chao_ace, by = "siteID")

#beetle_field_data = merge(diversity_index, beetle_field_data, by = "siteID")
#write.csv(beetle_field_data, "beetle_field_data.csv", row.names = FALSE)
#richness = data.frame(beetle_occ[, -c(2:467)])

beetle_diversity_indices = cbind(diversity_index, richness)

write.csv(beetle_diversity_indices, "beetle_div_indices.csv")
```


### Goal:
##### Run species richness for each site
##### Create data frame with different species for each site
##### Pseudoabundance is how many times the species is repeated (run for each site)
##### Count number of times a unique species occurs in each site

```{r}
bird_full_data = read.csv("input_data.files/bird_full_data.csv")

#Bird occurrence only sorted by siteID
#Quantify bird occurrence
#Group by specific epithet and site ID
bird_occ = bird_full_data %>%
  tabyl(taxonID, siteID, sort = TRUE)

#Show species distribution for each species for each site
bird_occ = data.frame(t(bird_occ))

#Place taxon as column labels
names(bird_occ) <- as.matrix(bird_occ[1,])
bird_occ = bird_occ[-1,] #remove the first line containing the taxonomic names
bird_occ[] <- lapply(bird_occ, function(x) type.convert(as.character((x))))

#Count the number of non-zero cells for each row
#This will give you the richness per site
#This will appear in the final column of the dataset
bird_occ$count <- rowSums(bird_occ!=0)

#Rename last column "count" as "species_richness"
names(bird_occ)[467] = "species_richness"

#Calculate abundance
#Sum all rows except species_richness column
row_sum = data.frame(rowSums(bird_occ[, -467]))

#Rename column
names(row_sum)[1] = "total_organisms"

#Rename 0th column
bird_occ<-tibble::rownames_to_column(bird_occ, "siteID") 

#Rename 0th column
row_sum<-tibble::rownames_to_column(row_sum, "siteID") 

#Merge row_sum dataframe with bird_occ dataframe by 
bird_occ = merge(bird_occ, row_sum,
                   by = "siteID",
                   all = TRUE, check.duplicates = FALSE)

#This table contains occurrence and richness values (last 2 columns)
```

##### Write Occurrence data to CSV file.
```{r}
write.csv(bird_occ, "bird_occ.csv", row.names = FALSE)
```

```{r}
#Merge info for interest site with site information data
bird_field_data = merge(bird_occ, site_info, by.x = "siteID", by.y = "field_site_id")
```

###### Create another dataframe which contains diversity information
###### Calculate Diversity indices using the Vegan Package in R
```{r}
bird_sp_div = t(bird_full_data %>%
  tabyl(taxonID, siteID, sort = TRUE))

#Convert to Data frame 
bird_sp_div = data.frame(bird_sp_div)


#Place specific epithet as row titles
names(bird_sp_div) <- as.matrix(bird_sp_div[1,])
bird_sp_div = bird_sp_div[-1,]
bird_sp_div[] <- lapply(bird_sp_div, function(x) type.convert(as.character((x))))


#Calculate Diversity Indices
#Simpson Diversity
simpson_diversity = data.frame(diversity(bird_sp_div, "simpson"))
simpson_diversity <-tibble::rownames_to_column(simpson_diversity, "siteID") 

#Shannon Diversity
shannon_diversity = data.frame(diversity(bird_sp_div, "shannon"))
shannon_diversity <-tibble::rownames_to_column(shannon_diversity, "siteID") 

#Merge all shannon and simpson diversity data tables
diversity_index = merge(shannon_diversity, simpson_diversity, by = "siteID")

#Rename diversity columns
names(diversity_index)[2] = "shannon"
names(diversity_index)[3] = "simpson"


bird_field_data = merge(diversity_index, bird_field_data, by = "siteID")
write.csv(bird_field_data, "bird_field_data.csv", row.names = FALSE)

#Import table into GIS and Make layers in GIS with species richness and total
#Number of species. This helps to visualize diversity.

#Merge richness and diversity indices
diversity = data.frame(bird_field_data[, c(1:3, 470:471)])
write.csv(richness, "bird_div_indices.csv")
```

###### Create another dataframe which contains diversity information
###### Calculate Diversity indices using the Vegan Package in R
```{r}
bird_full_data = read.csv("input_dta_files/bird_full_data.csv")

bird_sp_div = t(bird_full_data %>%
                    tabyl(taxonID, siteID, sort = TRUE))

#Convert to Data frame 
bird_sp_div = data.frame(bird_sp_div)


#Place specific epithet as row titles
names(bird_sp_div) <- as.matrix(bird_sp_div[1,])
bird_sp_div = bird_sp_div[-1,]
bird_sp_div[] <- lapply(bird_sp_div, function(x) type.convert(as.character((x))))
```

#Calculate Diversity Indices
```{r}
#Simpson Diversity
simpson_diversity = data.frame(diversity(bird_sp_div, "simpson"))
simpson_diversity <-tibble::rownames_to_column(simpson_diversity, "siteID") 

#Shannon Diversity
shannon_diversity = data.frame(diversity(bird_sp_div, "shannon"))
shannon_diversity <-tibble::rownames_to_column(shannon_diversity, "siteID") 

#Calculate Chao1 diversity
chao_ace = as.data.frame(estimateR(bird_sp_div))
chao_ace = t(chao_ace)
colnames(chao_ace)[2] = "Chao1_bird"
colnames(chao_ace)[4] = "ACE_bird"
chao_ace = as.data.frame(chao_ace[,c(2,4)])
chao_ace = tibble::rownames_to_column(chao_ace, "siteID") 

richness <- as.data.frame(rowSums(bird_sp_div!=0))
colnames(richness)[1] = "Richness_bird"

#Merge all diversity tables

diversity_index = merge(shannon_diversity, simpson_diversity, by = "siteID")

names(diversity_index)[2] = "Shannon_bird"
names(diversity_index)[3] = "Simpson_bird"

diversity_index = merge(diversity_index, chao_ace, by = "siteID")

#bird_field_data = merge(diversity_index, bird_field_data, by = "siteID")
#write.csv(bird_field_data, "bird_field_data.csv", row.names = FALSE)
#richness = data.frame(bird_occ[, -c(2:467)])

bird_diversity_indices = cbind(diversity_index, richness)

#write.csv(bird_diversity_indices, "bird_div_indices.csv")
```



###### Create another dataframe which contains diversity information
###### Calculate Diversity indices using the Vegan Package in R
```{r}
plant_full_data = read.csv("input_dta_files/plant_full_data.csv")

plant_sp_div = t(plant_full_data %>%
                    tabyl(taxonID, site, sort = TRUE))

#Convert to Data frame 
plant_sp_div = data.frame(plant_sp_div)


#Place specific epithet as row titles
names(plant_sp_div) <- as.matrix(plant_sp_div[1,])
plant_sp_div = plant_sp_div[-1,]
plant_sp_div[] <- lapply(plant_sp_div, function(x) type.convert(as.character((x))))
```

#Calculate Diversity Indices
```{r}
#Simpson Diversity
simpson_diversity = data.frame(diversity(plant_sp_div, "simpson"))
simpson_diversity <-tibble::rownames_to_column(simpson_diversity, "siteID") 

#Shannon Diversity
shannon_diversity = data.frame(diversity(plant_sp_div, "shannon"))
shannon_diversity <-tibble::rownames_to_column(shannon_diversity, "siteID") 

#Calculate Chao1 diversity
chao_ace = as.data.frame(estimateR(plant_sp_div))
chao_ace = t(chao_ace)
colnames(chao_ace)[2] = "Chao1_plant"
colnames(chao_ace)[4] = "ACE_plant"
chao_ace = as.data.frame(chao_ace[,c(2,4)])
chao_ace = tibble::rownames_to_column(chao_ace, "siteID") 

richness <- as.data.frame(rowSums(plant_sp_div!=0))
colnames(richness)[1] = "Richness_plant"

#Merge all diversity tables

diversity_index = merge(shannon_diversity, simpson_diversity, by = "siteID")

names(diversity_index)[2] = "Shannon_plant"
names(diversity_index)[3] = "Simpson_plant"

diversity_index = merge(diversity_index, chao_ace, by = "siteID")

#plant_field_data = merge(diversity_index, plant_field_data, by = "siteID")
#write.csv(plant_field_data, "plant_field_data.csv", row.names = FALSE)
#richness = data.frame(plant_occ[, -c(2:467)])

#plant_diversity_indices = cbind(diversity_index, richness)

write.csv(plant_diversity_indices, "plant_div_indices.csv")
```

```{r}
div = merge(plant_diversity_indices, bird_diversity_indices, by = "siteID")
div = merge(div, beetle_diversity_indices, by = "siteID")
write.csv(div, "diversity_index.csv")
```

###### There isn't a count for plants, it is more so a presence data
```{r}
#Plant occurrence only sorted by siteID
#Quantify plant occurrence
#Group by specific epithet and site ID
plant_occ = plant_full_data1 %>%
  tabyl(taxonID, siteID, sort = TRUE)


#Show species distribution for each species for each site
plant_occ = data.frame(t(plant_occ))

#Put first row as header row
names(plant_occ) <- as.matrix(plant_occ[1,])
plant_occ = plant_occ[-1,]
plant_occ[] <- lapply(plant_occ, function(x) type.convert(as.character((x))))

#Count the number of non-zero cells for each row
#This will give you the richness per site
#This will appear in the final column of the dataset
plant_occ$count <- rowSums(plant_occ!=0)

#Rename the last column "count" as species richness
names(plant_occ)[5625] = "species_richness"

#Calculate total number organisms
#Sum all rows except species_richness column
row_sum = data.frame(rowSums(plant_occ[, -5625]))

#rename column
names(row_sum)[1] = "total_organisms"

#rename 0th column
plant_occ<-tibble::rownames_to_column(plant_occ, "siteID") 

#rename 0th column
row_sum<-tibble::rownames_to_column(row_sum, "siteID") 

#merge row_sum dataframe with plant_occ dataframe by 
plant_occ = merge(plant_occ, row_sum,
                   by = "siteID",
                   all = TRUE, check.duplicates = FALSE)

#This new table now contains occurrence and richness values (last 2 columns)
```

###### Write Occurrence data to CSV file.
```{r}
write.csv(plant_occ, "plant_occ.csv", row.names = FALSE)
```

```{r}
#Merge site information for interest site with species data
plant_field_data = merge(plant_occ, site_info, by.x = "siteID", by.y = "field_site_id")

#Export previous file
write.csv(plant_field_data, "plant_field_data.csv", row.names = FALSE)

#We used these tables in ArcGIS Pro to Make layers with species richness and total
#number of species. This helps to visualize some of the diversity.
#Still have to figure out of to graph it
```

###### Create another dataframe which contains diversity information
###### Calculate Diversity indices using the Vegan Package in R
```{r}
plant_sp_div = t(plant_full_data1 %>%
  tabyl(taxonID, siteID, sort = TRUE))

#Convert to Data frame 
plant_sp_div = data.frame(plant_sp_div)


#Place specific epithet as row titles
names(plant_sp_div) <- as.matrix(plant_sp_div[1,])
plant_sp_div = plant_sp_div[-1,]
plant_sp_div[] <- lapply(plant_sp_div, function(x) type.convert(as.character((x))))

#Calculate Diversity Indices
simpson_diversity = data.frame(diversity(plant_sp_div, "simpson"))
simpson_diversity <-tibble::rownames_to_column(simpson_diversity, "siteID") 

#Shannon Diversity
shannon_diversity = data.frame(diversity(plant_sp_div, "shannon"))
shannon_diversity <-tibble::rownames_to_column(shannon_diversity, "siteID") 

#Merge all 3 diversity tables
diversity_index = merge(shannon_diversity, simpson_diversity, by = "siteID")

names(diversity_index)[2] = "shannon"
names(diversity_index)[3] = "simpson"

#merge richness (last 2 columns in plant_occ) and diversity indices
richness = plant_occ[, c(1,5626,5627)]
plant_diversity_indices = merge(diversity_index, richness, by = "siteID")
write.csv(plant_diversity_indices, "plant_div_indices.csv")
```