---
title: "NMDS for MDI"
author: "1st Author"
date: "2023-04-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load libraries
```{r, error = T}
#install.packages(c("funrar", "ecodist", "vegan", "ggplot2"))
library(funrar) #for relative abundance calculations
library(vegan)
library(ggplot2)
library(ecodist)
library(readr)
```

##### Download the multi/beetle/multi *_occ.csv files
###### Read CSV Files
```{r}
bird_occ <- read_csv("~/input_data_files/diversity_data/bird_occ.csv")
bird_occ = bird_occ[,-c(468,469)]

beetle_occ <- read_csv("~/input_data_files/diversity_data/beetle_occ.csv")
beetle_occ = beetle_occ[,-c(468,469)]

plant_occ <- read_csv("~/input_data_files/diversity_data/plant_occ.csv")
plant_occ = plant_occ[, -c(5626, 5627)]

#Merge Species occurrence data for all sites
multi_occ = merge(beetle_occ, bird_occ, by = "siteID")
multi_occ = merge(multi_occ, plant_occ, by = "siteID")

#write.csv(multi_occ, "multi_occ.csv")
```

##### Read in data with multi-trophic diversity and structural complexity data
```{r}
multi_div <- read.csv("md_str_11_10_2023.csv")

colnames(multi_div)[3] <- "plH" #plant shannon
colnames(multi_div)[4] <- "beH" #beetle shannon
colnames(multi_div)[5] <- "biH" #bird shannon
colnames(multi_div)[6] <- "md" #multi shannon

#Select the least correlated matrics, re corrplot
env_all = multi_div[,c("md", "lat", "lon", "MAP", "MAT", "r.._50m", "mmh.", "X40_95h", "rumple.", "VAI.", "dgf._100m")]

colnames(env_all)[1] <- "shannon_md"
colnames(env_all)[6] <- "cr"
colnames(env_all)[7] <- "mh"
colnames(env_all)[8] <- "h"
colnames(env_all)[9] <- "rum"
colnames(env_all)[10] <- "VAI"
colnames(env_all)[11] <- "dgf"

env_all = env_all[,c(2:11)]

#write.csv(env_all, "env_sites_new.csv")
#env_all will be used in all nmds plots
```

###### Working with multi Data First
####### Get Relative Abundance then make nmds plots
```{r}
# Make Matrix and calculate relative abundance of multitrophic diversity
matrix = as.matrix(multi_occ[,c(2:6557)])
abun = make_relative(matrix)

#write.csv(abun, "multidiv_abun.csv")

#Using vegan package let's get NMDS
nmds_multi = metaMDS(abun, engine = "monoMDS") 
plot(nmds_multi$points)

#See summary of NMDS
nmds_multi

#Plot stressplot
summary(stressplot(nmds_multi))
```

```{r}
#Make dataframe of nmds scores in preparation for ggplot2
site_scores = data.frame(scores(nmds_multi, "sites")) 
site_scores$siteID = multi_occ$siteID
site_scores

env_var = envfit(nmds_multi, env_all, permutations = 999)
env_var


#For continuous data
env_coord_cont =as.data.frame(scores(env_var, "vectors")) * ordiArrowMul(env_var) * 2 #multiplied by 2 to better see data

env_scores_sub <- cbind(env_coord_cont, pval = env_var$vectors$pvals) # add p-values to data frame

#All values were significant, but if they were not, I could plot the significant ones
#Subset for significant ones
sig_env <- subset(env_scores_sub, pval<=0.05)

rv1 = as.data.frame(env_var$vectors$r)
rv1 = as.data.frame(rv1[c(1:7,8),])

#Remove rows that were not significant
sig_env = cbind(sig_env, rv1)
colnames(sig_env)[4] = "R2"

#Add 0th column to the data frame
sig_env <- cbind(sig_env, env_str = rownames(sig_env))

#View significant variables
print(sig_env)
sig_env

#write.csv(sig_env, "sig_env_correlated.csv")
```

##### Plot NMDS
######Without labels
```{r}
tiff('nmds_nonlabel_wlegend.tiff', units="in", width = 10, height=6, res=600, compression = 'lzw')

#Plot
ggplot(data = site_scores, aes(x = NMDS1, y = NMDS2, color = env_all$forest_type)) + 
     geom_point(data = site_scores, aes(shape = env_all$forest_type, fill = env_all$forest_type), size = 10, alpha = 0.7) +
  stat_ellipse(linetype = 2, size = 1, alpha = 0.5) +
  scale_shape_manual(values = c(22, 24, 21)) +
     geom_segment(aes(x = 0, y = 0, xend = NMDS1, yend = NMDS2), 
      data = sig_env, size =1, alpha = 0.7, colour = "black") +
  scale_color_manual(values = c("Mixed" = "#00CCFF", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "#00CCFF", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
     #geom_text(data = sig_env, aes(x = NMDS1, y = NMDS2), size = 5, colour = "black", 
       #fontface = "bold", label = sig_env$env_str) +
     theme(axis.ticks.length = unit(-0.25, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_blank(), legend.key = element_blank())+ #, 
       #legend.title = element_text(size = 12, face = "bold", colour = "black"), 
       #legend.text = element_text(size = 10, colour = "black")) + 
     #labs(col = "Forest Type")
  #theme(legend.position = "left") +
  theme(text = element_text(size = 20), axis.text =  element_text(size = 20, color = "black")) +
  ylim(-5, 5) +
  xlim(-5, 5)

dev.off()
```

###### With labels
```{r}
tiff('nmds_labeled_wlegend.tiff', units="in", width = 10, height=6, res=600, compression = 'lzw')

#Plot
ggplot(data = site_scores, aes(x = NMDS1, y = NMDS2, color = env_all$forest_type)) + 
     geom_point(data = site_scores, aes(shape = env_all$forest_type, fill = env_all$forest_type), size = 10, alpha = 0.7) +
  stat_ellipse(linetype = 2, size = 1, alpha = 0.5) +
  scale_shape_manual(values = c(22, 24, 21)) +
     geom_segment(aes(x = 0, y = 0, xend = NMDS1, yend = NMDS2), 
      data = sig_env, size =1, alpha = 0.7, colour = "black") +
  scale_color_manual(values = c("Mixed" = "#00CCFF", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "#00CCFF", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
     geom_text(data = sig_env, aes(x = NMDS1, y = NMDS2), size = 5, colour = "black", 
       fontface = "bold", label = sig_env$env_str) +
     theme(axis.ticks.length = unit(-0.25, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_blank(), legend.key = element_blank())+ #, 
       #legend.title = element_text(size = 12, face = "bold", colour = "black"), 
       #legend.text = element_text(size = 10, colour = "black")) + 
     #labs(col = "Forest Type")
  #theme(legend.position = "left") +
  theme(text = element_text(size = 20), axis.text =  element_text(size = 20, color = "black")) +
  ylim(-5, 5) +
  xlim(-5, 5)

dev.off()

```

#### Conduct ANOSIM on NMDS Results to test if the pattern that we see (separation of forest type) is significant
```{r}
env_anosim = env_all[,11]

anosim_result = anosim(abun, env_anosim, distance = "bray", permutations = 9999)
summary(anosim_result)
plot(anosim_result, fill = "forest_type")

#ANOSIM result
print(anosim_result)

#Access R statistic
r_statistic <- anosim_result$statistic
print(paste("R statistic:", r_statistic))

#Access p-value
p_value <- anosim_result$signif
print(paste("p-value:", p_value))
```