---
title: "Linear Model for Structure v Diversity"
author: "1st Author"
date: "3/8/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Run Random Forest Model then do a LOOCV
#### Load libraries
```{r}
library(caret)
library(lme4)
install.packages("combinat")
library(combinat)
library(ggplot2)
library(tree)
library(class)
library(mgcv)
library(nlme)
library(devtools)
library(rfPermute)
library(gamclass)
library(caTools)
library(ModelMetrics)
library(modelr)
library(purrr)
library(tidyverse)
```

#### Read in data table containing diversity and structure data
```{r}
multi_div = read.csv("~/input_data_files/md_str_11_10_2023.csv")
```

##### Get subset of the multi_div dataset
##### This subset includes the significantly correlated metrics at respective scales
```{r}
#Select the least correlated metrics, along with latitude, longitude, MAT and MAP
#VAI, deep-gap fraction 100m, rumple, elevation rugosity 1m, Entropy at 50, combined rugosity at 60m

all_metrics = multi_div[,c("siteID", "forest_type", "MDI_Shannon", "lat", "lon", "MAP", "MAT", "r.._50m", "hr..", "mmh.", "X40_95h", "rumple.", "VAI.", "VCI._100m", "dgf._100m", "cf._100m", "E._50m", "tr._50m", "er.", "me._40m","maxe._60m", "sl._100m", "TRI.", "ro.")]

#write.csv(all_metrics, "all_metrics_full.csv")

sub1 = multi_div[,c("MDI_Shannon", "lat", "lon", "MAP", "MAT", "r.._50m", "mmh.", "X40_95h", "rumple.", "VAI.", "dgf._100m")]

colnames(sub1)[1] <- "shannon_md" #MDI
colnames(sub1)[6] <- "combined_complexity" #combined rugosity
colnames(sub1)[7] <- "mean_canopy_height"
colnames(sub1)[8] <- "max_height"
colnames(sub1)[9] <- "rumple"
colnames(sub1)[10] <- "VAI" #Vegetative Area Index
colnames(sub1)[11] <- "dgf" #Deepgap fraction
```

#### Run Linear Model
#### Look at all combinations of variables, select model with lowest AIC or error
```{r, error = T}
variables <- c("lat", "lon", "MAP", "MAT", "combined_complexity", "mean_canopy_height", "max_height", "rumple", "VAI")

# Generate all combinations of variable indices
all_combinations <- lapply(2:length(variables), function(k) combinat::combn(variables, k, simplify = FALSE))

# Fit linear models for combinations with fewer than 5 variables
models <- list()
model_count <- 0

for (combinations in all_combinations) {
  for (i in 1:length(combinations)) {
    variables_subset <- combinations[[i]]
    
    # Check the number of variables in the subset
    if (length(variables_subset) < 5) {
      formula <- as.formula(paste("shannon_md ~", paste(variables_subset, collapse = " + ")))
      
      # Use tryCatch to handle errors
      tryCatch({
        model <- gam(formula, data = sub1)
        models[[model_count + i]] <- list(formula = formula, model = model)
      }, error = function(e) {
        cat("Error occurred for combination:", paste(variables_subset, collapse = ", "), "\n")
      })
    }
  }
  model_count <- model_count + length(combinations)
}


# Initialize an empty list to store results

results_list <- list()

# Assuming 'models' is a list of model objects
for (i in 1:length(models)) {
  if (!is.null(models[[i]])) {
    # Extract the relevant information
    model_info <- list(
      Formula = as.character(models[[i]]$formula),
      AIC = models[[i]]$model$aic,
      RMSE = sqrt(mean(models[[i]]$model$residuals^2))
    )
    
    # Append the information to the results list
    results_list[[i]] <- model_info
  }
}

# Convert the list of results into a data frame
results_df <- do.call(rbind, results_list)

#write.csv(results_df, "lm_combinations.csv")
```

##### Run LOOCV on linear model 1
##### Linear model with lowest RMSE is investigated first
```{r}
set.seed(125)
 
# Perform LOOCV with Random Forest
loocv_results1 <- train(
  shannon_md ~ lon + MAP + combined_complexity + max_height,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results1)
```

##### Pull out predictions
```{r}
model1_pred = as.data.frame(loocv_results1$pred)


model1_pred = cbind(model1_pred, all_metrics$siteID)
model1_pred = cbind(model1_pred, all_metrics$forest_type)

colnames(model1_pred)[5] = "siteID"
colnames(model1_pred)[6] = "forest_type"

RMSE(model1_pred$obs, model1_pred$pred)
R2(model1_pred$pred, model1_pred$obs)
MAE(model1_pred$pred, model1_pred$obs)
```

##### Plot
```{r}
#tiff('lm_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')
ggplot(model1_pred, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "LM Predicted, lon, combined rug, mh, MAT", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.49, RMSE = 0.13") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))
#dev.off()
```

##### We will now model the linear model with the lowest AIC
##### Can run another LOOCV
```{r}
set.seed(128)

# Perform LOOCV with Random Forest
loocv_results2 <- train(
  shannon_md ~ lon + combined_complexity,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results2)
```

##### Look at observed vs fitted
```{r}
model2_pred = as.data.frame(loocv_results2$pred)

model2_pred = cbind(model2_pred, all_metrics$siteID)
model2_pred = cbind(model2_pred, all_metrics$forest_type)

colnames(model2_pred)[5] = "siteID"
colnames(model2_pred)[6] = "forest_type"

RMSE(model2_pred$obs, model2_pred$pred)
R2(model2_pred$pred, model2_pred$obs)
MAE(model2_pred$pred, model2_pred$obs)
```

##### Plot
```{r}
tiff('lm2_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')

ggplot(model2_pred, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "LM Predicted, lon, combined rug", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.51, RMSE = 0.13") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))

dev.off()
```

```{r}
lm = lm(MDI_Shannon ~ lon, data = all_metrics)
summary(lm)

model2_pred = as.data.frame(lm$fitted.values)

model2_pred = cbind(model2_pred, all_metrics$MDI_Shannon)

RMSE(model2_pred$`all_metrics$MDI_Shannon`, model2_pred$`lm$fitted.values`)

R2(model2_pred$`lm$fitted.values`, model2_pred$`all_metrics$MDI_Shannon`)
```
```{r}
lm = lm(MDI_Shannon ~ lat, data = all_metrics)
summary(lm)
```
```{r}
lm = lm(MDI_Shannon ~ MAP, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ MAT, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ X40_95h, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$mmh., data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$VAI., data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$rumple., data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$dgf._60m, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$sl._100m, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$maxe._100m, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$VCI._100m, data = all_metrics)
summary(lm)

lm = lm(MDI_Shannon ~ all_metrics$E._50m, data = all_metrics)
summary(lm)
```
