---
title: "Linear Models with Polynomial Expressions"
author: "1st Author"
date: "3/8/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Run Linear Models (02.521), then proceed to this .Rmd to add polynomial expressions, running LOOCV
#### LM with Shannon_md ~ longitude^3 + combined rugosity was the best out of all 3 models

##### Load libraries
```{r}
library(caret)
library(lme4)
library(combinat)
library(ggplot2)
library(tree)
library(class)
library(mgcv)
library(nlme)
library(devtools)
library(rfPermute)
library(gamclass)
library(caTools)
library(ModelMetrics)
library(modelr)
library(purrr)
library(tidyverse)
```

#### Read in data table containing diversity and structure data
```{r}
multi_div = read.csv("md_str_11_10_2023.csv")
```

##### Get subset of the multi_div dataset
##### This subset includes the significantly correlated metrics at respective scales
```{r}
#Select the least correlated metrics, along with latitude, longitude, MAT and MAP
#VAI, deep-gap fraction 100m, rumple, elevation rugosity 1m, Entropy at 50, combined rugosity at 60m

sub1 = multi_div[,c("MDI_Shannon", "lat", "lon", "MAP", "MAT", "r.._50m", "mmh.", "X40_95h", "rumple.", "VAI.", "dgf._100m")]

colnames(sub1)[1] <- "shannon_md" #MDI
colnames(sub1)[6] <- "combined_complexity" #combined rugosity
colnames(sub1)[7] <- "mean_canopy_height"
colnames(sub1)[8] <- "max_height"
colnames(sub1)[9] <- "rumple"
colnames(sub1)[10] <- "VAI" #Vegetative Area Index
colnames(sub1)[11] <- "dgf" #Deepgap fraction
```


##### Deciding on what degree of polynomial to choose
#####  test the null hypothesis that a model is sufficient to explain the data against the alternative hypothesis that another is required
```{r}
lm1 = lm(shannon_md ~ lon + MAT + combined_complexity + max_height, data = sub1)

plm1 = lm(shannon_md ~ poly(lon, 2) + MAT + combined_complexity + max_height, data = sub1)

plm2 = lm(shannon_md ~ poly(lon, 3) + MAT + combined_complexity + max_height, data = sub1)

plm3 = lm(shannon_md ~ poly(lon, 3) + poly(MAT,2) + combined_complexity + max_height, data = sub1)

plm4 = lm(shannon_md ~ poly(lon, 2) + poly(MAT,2) + combined_complexity + max_height, data = sub1)

plm5 = lm(shannon_md ~ poly(lon, 2) + poly(MAT,3) + combined_complexity + max_height, data = sub1)

plm6 = lm(shannon_md ~ poly(lon, 4) + poly(MAT,2) + combined_complexity + max_height, data = sub1)

summary(plm3)
summary(plm6)

print(anova(lm1, plm1, plm2, plm3, plm4, plm5, plm6))
```


##### plm3 seems to be the best
##### Run LOOCV on linear model plm3
```{r}
set.seed(125)

# Perform LOOCV with Random Forest
loocv_results1 <- train(
  shannon_md ~ poly(lon, 3) + poly(MAT, 2) + combined_complexity + max_height,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results1)
```

##### Pull our predictions
```{r}
pred_model1 = loocv_results1$pred

pred_model1 = cbind(pred_model1, all_metrics$siteID)
pred_model1 = cbind(pred_model1, all_metrics$forest_type)

colnames(pred_model1)[5] = "siteID"
colnames(pred_model1)[6] = "forest_type"

RMSE(pred_model1$obs, pred_model1$pred)
R2(pred_model1$pred, pred_model1$obs)
MAE(pred_model1$pred, pred_model1$obs)
```

##### Plot
```{r}
#tiff('loocv_plm1_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')
ggplot(pred_model1, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "LM Predicted, lon, combined rug, mh, MAT", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.58, RMSE = 0.12") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))
#dev.off()
```

##### We will now model the linear model with the lowest AIC
##### Can run LOOCV
```{r}
set.seed(128)

# Perform LOOCV with Random Forest
loocv_results2 <- train(
  shannon_md ~ poly(lon, 3) + combined_complexity,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results2)
```

##### Look at observed vs fitted
```{r}
pred_model2 = loocv_results2$pred

pred_model2 = cbind(pred_model2, all_metrics$siteID)
pred_model2 = cbind(pred_model2, all_metrics$forest_type)

colnames(pred_model2)[5] = "siteID"
colnames(pred_model2)[6] = "forest_type"

RMSE(pred_model2$obs, pred_model2$pred)
R2(pred_model2$pred, pred_model2$obs)
MAE(pred_model2$pred, pred_model2$obs)
```

##### Plot
```{r}
tiff('loocv_plm_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')
ggplot(pred_model2, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "LM Predicted, lon3, combined rug", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.68, RMSE = 0.11") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))
dev.off()
```

```{r}
set.seed(128)

# Perform LOOCV with Random Forest
loocv_results2 <- train(
  shannon_md ~ poly(lon, 3) + combined_complexity,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results2)
```

```{r}
set.seed(128)

# Perform LOOCV with Random Forest
loocv_results2 <- train(
  shannon_md ~ poly(lon, 2) + poly(MAP, 2) + MAT,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results2)
```

##### Look at observed vs fitted
```{r}
pred_model2 = loocv_results2$pred

pred_model2 = cbind(pred_model2, all_metrics$siteID)
pred_model2 = cbind(pred_model2, all_metrics$forest_type)

colnames(pred_model2)[5] = "siteID"
colnames(pred_model2)[6] = "forest_type"

RMSE(pred_model2$obs, pred_model2$pred)
R2(pred_model2$pred, pred_model2$obs)
MAE(pred_model2$pred, pred_model2$obs)
```

##### Plot
```{r}
tiff('loocv_geoenv_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')
ggplot(pred_model2, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "PRM Predicted, lon3, map2, mat", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.41, RMSE = 0.16") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))
dev.off()
```

```{r}
set.seed(128)

# Perform LOOCV with Random Forest
loocv_results2 <- train(
  shannon_md ~ poly(lon, 2) + MAT + poly(MAP,2) + combined_complexity,
  data = sub1,
  method = "lm",
  trControl = trainControl(method = "LOOCV")
)

print(loocv_results2)
```

##### Look at observed vs fitted
```{r}
pred_model2 = loocv_results2$pred

pred_model2 = cbind(pred_model2, all_metrics$siteID)
pred_model2 = cbind(pred_model2, all_metrics$forest_type)

colnames(pred_model2)[5] = "siteID"
colnames(pred_model2)[6] = "forest_type"

RMSE(pred_model2$obs, pred_model2$pred)
R2(pred_model2$pred, pred_model2$obs)
MAE(pred_model2$pred, pred_model2$obs)
```

```{r}
write.csv(all_metrics, "all_metrics.csv")
```

##### Plot
```{r}
tiff('loocv_geoenvcc_str_div.tiff', units="in", width = 10, height=8, res=600, compression = 'lzw')
ggplot(pred_model2, aes(x = obs, y = pred, color = forest_type)) +
  geom_smooth(method = "lm", aes(fill = forest_type, col = forest_type), alpha = 0.2, linetype = "dashed") + 
  geom_point(aes(shape = forest_type, fill = forest_type), size = 12, alpha = 0.7) +
  scale_shape_manual(values = c(22, 24, 21)) + 
  scale_color_manual(values = c("Mixed" = "cyan4", "Deciduous" = "deeppink",
                                "Evergreen" = "darkgreen")) +
  scale_fill_manual(values = c("Mixed" = "cyan3", "Deciduous" = "#E7298A",
                                "Evergreen" = "darkgreen")) +
  geom_abline(size = 1) +
  theme(axis.ticks.length = unit(-0.2, "cm"), axis.title = element_text(size = 20, face = "bold", colour = "black"), 
       panel.background = element_blank(), panel.border = element_rect(fill = NA, colour = "black"), 
       axis.text = element_text(face = "bold", size = 15, colour = "black"), legend.key = element_blank()) +
  labs(title = "PRM Predicted, lon3, map2, mat", x = "Observed", y =  "Predicted") +
  annotate("text", x = 0.3, y = 0.9, label = "R2 = 0.61, RMSE = 0.12") +
  scale_x_continuous(expand = c(0, 0), limits = c(0,1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0,1))
dev.off()
```

